%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contents: No Input Device
% $Id: typeset.tex 537 2015-07-18 09:43:10Z oetiker $
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\chaptername}{Section}
\chapter{No Input Device}

\begin{intro}
  This section outlines \emph{MantaMate} presets when using no HOST device.
\end{intro}

NO DEVICE ATTACHED
(all presets include a clock out trigger on output A1)

\section{Presets}

  Each of the \emph{MantaMate} presets has a clock output on the A1 output.
  The remainder of the outputs vary as follows:

  \textbf{0}
  11 Random voltages on each clock

  \textbf{1}
  11 Random Gates on each clock

  \textbf{2}
  11 Random Triggers on each clock

  \textbf{3}
  Consecutive integer dividers -- random voltages

  \textbf{4}
  Consecutive integer dividers -- gates

  \textbf{5}
  Consecutive integer dividers -- triggers

  \textbf{6}
  Consecutive integer dividers -- toggles

  \textbf{7}
  Power of 2 dividers -- random voltages

  \textbf{8}
  Power of 2 dividers -- gates

  \textbf{9}
  Power of 2 dividers -- triggers

  \textbf{10}
  Power of 2 dividers -- toggles

  \textbf{Presets 11-18 use randomly generated patterns that repeat}

  \textbf{11}
  All patterns same length -- random voltages

  \textbf{12}
  All patterns same length -- gates

  \textbf{13}
  All patterns same length -- triggers

  \textbf{14}
  All patterns same length -- toggles

  \textbf{15}
  Each pattern has its own random length -- random voltages

  \textbf{16}
  Each pattern has its own random length -- gates

  \textbf{17}
  Each pattern has its own random length -- triggers

  \textbf{18}
  Each pattern has its own random length -- toggles

  \textbf{19-99}
  User storable presets (save the randomly generated patterns)


  The No Device functionality is activated by pressing the up or down button
  while no device is plugged into the MantaMate.
  It will then continue until power is turned off or a device is plugged in.

  The repeating random patterns are generated on power-up.
  Each of the 11 available outputs has its own pattern that is 32 steps long.

  You can generate new ones by holding down the Preferences button and then
  pressing the up or down buttons.

  Pressing up results in a compeletely new random pattern.
  Pressing down subtly changes the current patterns.

  There is a Pattern Length parameter that is set by going into the first
  preference menu (tuning) and pressing S to get to the sub-menu.
  You can then alter the length parameter.
  In the case of the "all patterns same length" presets,
  this Pattern Length enforces the reset of all patterns,
  so that they all cycle at the same time.
  In the case of "each pattern has its own random length"
  presets, the Pattern Length is treated as a "maximum pattern length"
  and will reset any patterns that are not already repeating in a shorter
  time period. The value defaults to 16, and valid values are 1-32.


% Local Variables:
% TeX-master: "lshort2e"
% mode: latex
% mode: flyspell
% End:
